figures and calculations for global fisheries management

### 2019-01-19 documents/figs-and-calcs.Rmd
commit to pull
figure tweeks

theme_set(theme_ipsum(base_size = 14))

@@

@@

figure_4 <- demo %>% 
  filter(tolower(metric) %in% c("profits", "costs", "revenue")) %>% 
  ggplot() + 
  geom_line(aes(biomass,value, color = metric), size = 2) + 
  ggsci::scale_color_simpsons(name = "") + 
  theme_classic() + 
  labs(y = "Value", x = "Fish Biomass") + 
  geom_vline(aes(xintercept = b_oa * k / 2), color = "red", linetype = 2) + 
  geom_vline(aes(xintercept = b_mey), color = "blue", linetype = 2) + 
  scale_x_continuous(expand = c(0,0)) + 
  scale_y_continuous(expand = expand_scale(mult = 0, add = c(0, .2)), limits = c(0,NA),
                     breaks = c(0,max(demo$value)), labels = c("Low","High"))

@@

figure_6 <- results %>%
  filter(year == max(year)) %>%
  ggplot() +
  geom_raster(aes(cost, discount, fill = b / (k/2)),
              interpolate = TRUE) +
  scale_x_continuous(
    expand = c(0, 0),
    breaks = c(min(scenes$cost), 750, 1500),
    labels = c("Low", "Medium", "High"),
    name = "Fishing Costs"
  ) +
  scale_y_continuous(expand = c(0, 0),
                     name = "Discount Rate",
                     labels = scales::percent) +
  scale_fill_gradient2(
    low = "tomato",
    mid = "white",
    high = "steelblue",
    midpoint = 1,
    name = "Bmey",
    guide = guide_colorbar(frame.colour = "black",
                           barheight = unit(15, "lines")),
    limits = c(0,2)
  ) + 
  theme(panel.border = element_rect(color = "black",
                                    fill = "transparent"))

@@

@@

#add the turf data to upside
projection_turfs <- full_join(projection_data, turfs, by = c("clean_country", "SciName", "SpeciesCat","Year"), all = T) %>% 
  mutate(turf = ifelse(is.na(turf),0,1)) %>% 
  mutate(CatchShare = ifelse(turf == 1,2, CatchShare)) %>%
  left_join(coops %>% select(SciName, clean_country, cooperative), by = c("SciName", "clean_country")) %>% 
  left_join(gdp, by = "clean_country") %>% 
    mutate(turf = ifelse(cooperative == 1,1,turf))

projection_turfs %>% 
  filter(Year == 2012) %>% 
  group_by(CatchShare) %>% 
  summarise(tc = sum(Catch, na.rm = T))

@@

itq_broad_fit <-
  glm(
    formula = CatchShare ~ gdp_center + MainCat + log(MSY),
    family = "binomial",
    data = downjoin
  )

@@

cs_or_turf_fit <-
  glm(
    formula = TURF ~ gdp + SpeciesCatName,
    family = "binomial",
    data = catch_shares_and_turfs 
  )

>>>>

theme_set(theme_ipsum(base_size = 16) + theme(axis.title.x = element_text(size = 18), axis.title.y = element_text(size = 18)))

@@

projection_spatial <-  projection_spatial %>% 
    st_transform(crs = "+proj=moll +datum=WGS84")

@@

labels <- demo %>% 
  spread(metric,value) %>% 
  mutate(oa = abs(Costs - Revenue))

oa_y <- labels$Costs[labels$oa == min(labels$oa)][1]

profits_y <- labels$Costs[labels$Profits == max(labels$Profits)][1]

labs <- dplyr::tibble(x = c(b_oa * k / 2,b_mey),
                      y = c(oa_y, profits_y),
                      labs = c("A","B"))

figure_4 <- demo %>% 
  filter(tolower(metric) %in% c("profits", "costs", "revenue")) %>% 
  ggplot() + 
  geom_line(aes(biomass,value, color = metric), size = 2) + 
  ggsci::scale_color_simpsons(name = "") + 
  theme_classic() + 
  labs(y = "Value", x = "Fish Biomass") + 
  geom_vline(aes(xintercept = b_oa * k / 2), color = "red", linetype = 2) + 
  geom_vline(aes(xintercept = b_mey), color = "blue", linetype = 2) + 
  scale_x_continuous(expand = c(0,0)) + 
  scale_y_continuous(expand = expand_scale(mult = 0, add = c(0, .2)), limits = c(0,NA),
                     breaks = c(0,max(demo$value)), labels = c("Low","High")) + 
  ggrepel::geom_text_repel(data = labs,aes(x, y, label = labs),
                            force =  20, size = 10)

@@

figure_6 <- results %>%
  filter(year == max(year)) %>%
  ggplot() +
  geom_raster(aes(cost, discount, fill = b / (k/2)),
              interpolate = TRUE) +
  scale_x_continuous(
    expand = c(0, 0),
    breaks = c(min(scenes$cost), 750, 1500),
    labels = c("Low", "Medium", "High"),
    name = "Fishing Costs"
  ) +
  stat_contour(breaks=c(1),aes(cost, discount, z = b / (k/2)), color ="black")+
  scale_y_continuous(expand = c(0, 0),
                     name = "Discount Rate",
                     labels = scales::percent) +
  scale_fill_gradient2(
    low = "tomato",
    mid = "white",
    high = "steelblue",
    midpoint = 1,
    name = "Bmey",
    guide = guide_colorbar(frame.colour = "black",
                           barheight = unit(15, "lines")),
    limits = c(0,2)
  ) + 
  theme(panel.border = element_rect(color = "black",
                                    fill = "transparent"))

@@

prices <- read_csv(here("data", "Exvessel Price Database.csv")) %>%
  janitor::clean_names() %>%
  rename(scientificname = scientific_name) %>%
  mutate(log_exvessel = log(exvessel)) %>%
  group_by(asfis_species, pooled_commodity, group_for_pairing) %>%
  mutate(lag_exvessel = lag(exvessel)) %>%
  ungroup()

@@

#add the turf data to upside
projection_turfs <-
  full_join(
    projection_data,
    turfs,
    by = c("clean_country", "SciName", "SpeciesCat", "Year"),
    all = T
  ) %>%
  mutate(turf = ifelse(is.na(turf), 0, 1)) %>%
  left_join(
    coops %>% select(SciName, clean_country, cooperative),
    by = c("SciName", "clean_country")
  ) %>%
  mutate(cooperative = ifelse(is.na(cooperative), 0, 1)) %>%
  left_join(gdp, by = "clean_country") %>%
  mutate(CatchShare = ifelse(is.na(CatchShare), 0, CatchShare)) %>%
  mutate(CatchShare2 = dplyr::case_when(CatchShare == 1 ~ 1,
                                        turf == 1 ~ 2,
                                        cooperative == 1 ~ 3,
                                        TRUE ~ 0)) %>%
  mutate(turf = ifelse(cooperative == 1, 1, turf)) %>%
  mutate(CatchShare = ifelse(turf == 1, 2, CatchShare)) %>%
  left_join(prices, by = c("SciName" = "scientificname", 'Year' = 'year')) %>%
  filter(Year == 2012) %>%
  group_by(CatchShare) %>%
  mutate(Catch = ifelse(is.na(Catch), mean(Catch, na.rm = TRUE), Catch)) %>%
  ungroup()

projection_turfs %>% 
  filter(Year == 2012) %>% 
  group_by(CatchShare2) %>% 
  summarise(tc = sum(Catch, na.rm = T)) %>% 
  mutate(pcatch = scales::percent(tc / 80e6, accuracy = 1))

@@

itq_broad_fit <-
  glm(
    formula = CatchShare ~ gdp_center + MainCat + log(MSY) + exvessel,
    family = "binomial",
    data = downjoin
  )

@@

cs_or_turf_fit <-
  glm(
    formula = TURF ~ gdp + SpeciesCatName + Catch,
    family = "binomial",
    data = catch_shares_and_turfs 
  )
